---
title: "Weight of Fish"
author: "Denise Sahagun"
date: "April 2021"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
Allfish <- read.csv(file = "Fish.csv")
Allfish$Species <- as.factor(Allfish$Species)
levels(Allfish$Species)
```

```{r}
Perch <- subset(Allfish,Species == "Perch")
Perch <- select(Perch, -Species) 
Bream <- subset(Allfish, Species == "Bream")
Bream <- select(Bream, -Species)
Smelt <- subset(Allfish,Species == "Smelt")
Smelt <- select(Smelt, -Species)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

## Build the best regression model you can that predicts the weight of perch
## Using only two predictor variables  


# Perch
``````{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

This plot shows the best regression model is height and width.

##Which is best??  

```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[2,]
```

```{r}
Perchmodel <- lm(Weight~Height+Width ,data= Perch)
summary.lm(Perchmodel)
```

The model has adjusted r^2 which is 0.94, the best model is high the standard error is 85.17

# Bream

``````{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Bream,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

 The plot above shows the three best models is length,height, and width.

##Which is best??  

```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[2,]
```

```{r}
Breammodel <- lm(Weight~Height+Length2 ,data= Bream)
summary.lm(Breammodel)
```

The adjusted r^2 is 0.9356 and the residual standard error is 53.1

# Smelt

``````{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Smelt,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

This plot shows the best regression model is height, Length and width.

##Which is best??  

```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[2,]
```

```{r}
Smeltmodel <- lm(Weight~Height+Length2 ,data= Smelt)
summary.lm(Smeltmodel)
```

The adjusted R^2 is 0.9507 and the residual standard error is 0.9968
